Questions to Developers

### 2020-11-29 StateOfPractice/Methodology/Questions to Developers.tex
cleaned up Methodology appendix, moved one part to Questions to Devs

>>>>

\subsection{Old notes from methodology: Information about the software}
Compare to questions above and then delete this subsection

\begin{enumerate}
	\item \ad{General} What is the most important software quality(ies) to your
	work? (set of selected qualities plus "else")
	\item \ad{General} Are there any examples where the documentation helped? If
	yes, how it helped. ({yes$^*$, no})
	\item \ad{General} Is there any documentation you feel you should produce and do
	not? If yes, what is it and why? ({yes$^*$, no})
	\item \ad{Completeness} Do you address any of your quality concerns using
	documentation? If yes, what are the qualities and the documents. ({yes$^*$,
		no})
	\item \ad{Visibility/Transparency} Is there a certain type of development
	methodologies used during the development? (\{Waterfall, Scrum, Kanban,
	else\})
	\item \ad{Visibility/Transparency} Is there a clearly defined development
	process? If yes, what is it. (\{yes$^*$, no\})
	\item \ad{Visibility/Transparency} Are there any project management tools used
	during the development? If yes, what are they. (\{yes$^*$, no\})
	\item \ad{Visibility/Transparency} Going forward, will your approach to
	documentation of requirements and design change? If not, why not. (\{yes,
	no$^*$\})
	\item \ad{Correctness and Verifiability} During the process of development, what
	tools or techniques are used to build confidence of correctness? (string)
	\item \ad{Correctness and Verifiability} Do you use any tools to support
	testing? If yes, what are they. (e.g. unit testing tools, regression testing
	suites) (\{yes$^*$, no\})
	\item \ad{Correctness and Verifiability} Is there any document about the
	requirements specifications of the program? If yes, what is it. (\{yes$^*$,
	no\})
	\item \ad{Portability} Do you think that portability has been achieved? If yes,
	how? (\{yes$^*$, no\})
	\item \ad{Maintainability} How was maintainability considered in the design?
	(string)
	\item \ad{Maintainability} What is the maintenance type? (set of \{corrective,
	adaptive, perfective, unclear\})
	\item \ad{Reusability} How was reusability considered in the design? (string)
	\item \ad{Reusability} Are any portions of the software used by another package?
	If yes, how they are used. ({yes$^*$, no})
	\item \ad{Reproducibility} Is reproducibility important to you? ({yes$^*$, no})
	\item \ad{Reproducibility} Do you use tools to help reproduce previous software
	results? If yes, what are they. (e.g. version control, configuration
	management) ({yes$^*$, no})
	\item \ad{Completeness} Is any of the following documents used during the
	development? ({yes$^*$, no})
	\item \ad{General} Will this experience influence how you develop software? Do
	you see yourself maintaining the same level of documentation, tool support as
	you go forward? (string)
	\begin{itemize}
		\item Module Guide
		\item Module Interface Specification
		\item Verification and Validation Plan
		\item Verification and Validation Report
	\end{itemize}
\end{enumerate}
